TBD

### 2021-02-19 outputs/paper/paper.Rmd
Plots/statistical tests re-ordered by category
Next step: clean stat test tables + analysis writeup.

@@

@@

kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

@@

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

@@

## Statistical Tests

```{r statistical tests, echo = FALSE, message = FALSE}
### Welch's T-Test

# Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
tidy(t.test(control_q5, treatment_q5))

#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
tidy(t.test(control_q6, treatment_q6))

### Paired T-Test

tidy(t.test(all_simulated_dataset$Q5,
       all_simulated_dataset$Q6,
       paired=TRUE,
       conf.level = 0.95))

# Chi-Square

#Q7

q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type)
tidy(chisq.test((q7_chi)))

#Q8

q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type)
tidy(chisq.test((q8_chi)))

#Q10

q10_chi <- table(all_simulated_dataset$Q10, all_simulated_dataset$type)
tidy(chisq.test((q10_chi)))

#Q12

q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type)
tidy(chisq.test((q12_chi)))

#Q14

q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type)
tidy(chisq.test((q14_chi)))
```

>>>>

## Sample Characteristics

@@

## Effects of Intervention on Number of Employees

@@

kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))

### T-Tests (Welch's)

# Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t.test(control_q5, treatment_q5)

#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t.test(control_q6, treatment_q6)

```

## Effects of Intervention on Revenue

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type)
chisq.test(q7_chi)

```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type)
chisq.test(q8_chi)

```

@@

@@

## Effects on Menu Prices

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

q10_chi <- table(all_simulated_dataset$Q10, all_simulated_dataset$type)
chisq.test(q10_chi)
```

## Effects on Hours/Days of Operation

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type)
chisq.test(q12_chi)
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type)
chisq.test(q14_chi)
```

@@
